Barneby Lives usage example

### 2023-05-18 scripts/project_template.Rmd
grab input date columns for relocation

```{r dummy data}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 1000), seq(1:1000)),
  day = c(sample(1:31, size = 1000, replace = T)),
  month = c(sample(5:10, size = 1000, replace = T)),
  year = 2023,
  datum = sample(c('nad83', 'nad27', 'wgs84'), size = 1000, replace = T),
  longitude = runif(1000, min = -120, max = -100), 
  latitude = runif(1000, min = 35, max = 48)
)

@@

out <- dms2dd(dummy_pts)
d <- coords2sf(out)

@@

fourtet <- data.frame(col_date = c('12/23/2003','07/09/2023', '1/13/2016'),
                      det_date = c('12/25/2003','07/09/2023', '1/13/2016'),
                      tet = c('abc', 'def', 'ggg'))

date_parser(fourtet, coll_date = 'col_date', det_date = 'det_date')

@@

```{r Acquire administrative geodata}

@@

>>>>

```{r dummy data}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 1000), seq(1:1000)),
  day = c(sample(1:30, size = 1000, replace = T)),
  month = c(sample(5:10, size = 1000, replace = T)),
  year = 2023,
  datum = sample(c('nad83', 'nad27', 'wgs84'), size = 1000, replace = T),
  longitude = runif(1000, min = -120, max = -100), 
  latitude = runif(1000, min = 35, max = 48)
) %>% 
  mutate(col_date = paste(month, day, year, sep = "/"))

@@

out <- dms2dd(dummy_pts)
out <- coords2sf(out)

@@

out <- date_parser(out, coll_date = 'col_date')

@@

```{r Acquire geodata}

@@

```{r gather taxonomic data}
